Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2022-07-07 Journal1/Response3/Response.tex

\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment1:} ``However, the paper still needs some improvement in terms of readability. Some paragraphs are too long  ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We have changed the paper's introduction and checked the text entirely according to this comment.
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment2:} `` the figures are difficult to locate from their reference in the text (figures at top, as typical IEEE template is better), the text in the figures is too small ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
Thank you for this comment. We changed the paper's figures totally according to this comment.
\begin{longtable}{|p{0.975\textwidth}|}
\hline \hline
\RaggedRight
\cellcolor{gray!15}
\textbf{\noindent Comment3:} ``the contributions discussed in the introduction are not easily found in the other parts of the paper.  ''\\
\hline
\end{longtable}
\vspace*{-1\baselineskip}
\noindent \textbf{Response:\\}
We thank the reviewer for adding clarity to our paper and reducing ambiguity in this condition.  We changed the contribution in a better way based on this comment. We have removed some sentences and rewritten the contribution in order to our paper's section.
Below we write the whole contribution section.

This paper aims to optimize the resource utilization of a downlink O-RAN system to develop an isolated network slicing outline for the three 5G service classes.
We use mathematical methods to decompose and convexify the problem and solve it using hierarchical algorithms.
%Our paper focuses on the multi-service resource management of the RAN slicing in an open and flexible O-RAN architecture.}
%In this paper, as depicted in Figure \ref{fig:c11}, the downlink of the O-RAN system is studied.
 The main contributions of this paper are summarized as follows:
\begin{itemize}
\item We examine the problem of radio resource allocation and VNF activation within the O-RAN architecture.
Based on the three types of 5G service classes, i.e., eMBB, URLLC and mMTC, and their corresponding QoS requirements and service priorities, we formulate a problem for allocating baseband resources such as power, physical resource blocks (PRBs), O-RUs, and activating VNFs to maximize the weighted throughput of the O-RAN.
\item We propose a two-step resource management algorithm for solving the optimization problem.
In the first step, we reformulate and simplify the problem so as to find an upper and lower bound for the number of activated VNFs. Moreover, we use the Lagrangian function and Karush-Kuhn-Tucker (KKT) conditions to obtain the optimal power and PRB allocation. In the second step, the problem of O-RU association is converted to a multiple knapsack problem and solved by a greedy algorithm.
\item We provide insights into the complexity of the proposed algorithms and demonstrate their convergence. Additionally, we analyze the feasibility region of our problem and introduce a fast algorithm to check its feasibility numerically.
\item We show via numerical results that the proposed algorithm outperforms two baseline schemes, in terms of achievable data rate. Remarkably, the proposed algorithm performs close to the optimal solution in low-interference conditions.
\end{itemize}

### 2022-07-07 Journal1/paper5TNSM/pr.tex
Add file

\begin{figure}
  \centering
  \captionsetup{justification=centering}
    %\includegraphics[scale = 0.45]{finalDraw.pdf}
    \includegraphics[width=9.5cm,height=6cm]{finalDraw1.pdf}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Network sliced O-RAN system}
  \label{fig:c11}
\end{figure}
\subsection{Motivation}
\textcolor{MidnightBlue}{The problem of finding the optimal resource allocation, independently of the specific RAN technology, is vital for reducing the cost of the system and improving the QoS of the user equipments (UEs). In case of 5G systems, there are many related significant challenges such as interference alignment, limited capacity of fronthaul links, energy restrictions on virtual machines, etc \cite{lee2018dynamic,SystemCostMinimization, setayesh2020joint}.}

@@

Multiplexing eMBB and URLLC services on the same RAN is particularly challenging, which has motivated some recent works.
In \cite{setayesh2020joint,yang2020should,saggese2021power}, the problem of resource allocation in the coexistence of URLLC and eMBB services is considered based on their QoS.
In \cite{alsenwi2021intelligent}, the problem of resource allocation for joint eMBB and URLLC services is formulated and solved by deep reinforcement learning.
 In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services. The system guarantees latency, service rate, and reliability maintenance.

In \cite{SystemCostMinimization,guo2016exploiting}, the authors address the issue of beamforming and VMs activation (using virtualization) in a C-RAN system with limited fronthaul capacity.
This paper aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint.
Also, transmission and processing delays are modeled based on M/M/1 queueing theory to guarantee UE delays.
In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated; Also, the association of RRH to the UE is considered and solved using innovative methods.

In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in the H-CRAN system is considered to maximize energy efficiency.
In \cite{amani2019power}, optimum power is obtained in massive MIMO aided C-RAN. Also, the problem of RRH to BBU and the RRH to UE association is obtained.

@@

A UE in an O-RU $r$ using PRB $k$ receives interference from other O-RUs in the set of $r' \in R \not\in r$ that are using the same PRB $k$. Two types of interference occur between UEs in each slice; the first is inter-slice interference between UEs of different slices, and the second is intra-slice interference between UEs of the same slice that is shown in Figure \ref{fig:intf}.

Network Slicing techniques significantly reduce inter-service interference.
Some methods apply the network slicing technique in PRB scheduling to isolate PRBs in slices and remove inter-slice interference. One of these methods is to have two-time scale scheduling. The PRB scheduling to the slices is performed on the first time scale, and on the second time scale, the PRB scheduling to the UEs of slices is carried out. Since there are limited resources, inter-service interference cannot be eliminated entirely. The other method is to allocate part of the RB of eMBB services to URLLC, and mMTC \cite{alsenwi2021intelligent, setayesh2020joint, mei2021intelligent}. In this paper, we assume that the PRB scheduling is performed. Also, in subsection \ref{prb}, we briefly study the PRB scheduling between slices.
\begin{figure}
  \centering
  \captionsetup{justification=centering}
    \includegraphics[scale = 0.35]{Interference.png}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Type of Interference Signal}
  \label{fig:intf}
\end{figure}
 $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise represented as
%{\color{red} use paranthesis in the following equation to clear +}
\begin{subequations}\label{eqI}
\begin{alignat}{4}
&I_{r,u(s,i)}^{k} =\\
 &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\\
&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
\end{alignat}
\end{subequations}
%{\color{red} $\gamma_1$ is constant used instead of variable. }
%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
where $e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU. %($\gamma_1$ and $\gamma_2$ are two variales. You  define on variable here.)
Furthermore, there is no inter-slice interference since slices are isolated. Therefore, there exist only intra-slice interference.

@@

Moreover, ${x_P}$ denotes the precoded message before compression, and ${x_Q}$ illustrates the precoded message after compression shown in Figure \ref{fig:pq}.

@@

\begin{equation}\label{eq3}

@@

\mathcal{R}_{u(s_1,i)}^{r} &= \sum_{k=1}^{K} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}} e^k_{r,u(s_1,i)}),\\
\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{r} g^r_{u(s_1,i)},

@@

So, we assume that the total delay is approximate to the processing delay ($T^{\text{\text{tot}}} \approx T^{\text{proc}}$).
%Here we assume the propagation delay and the transmission delay are negligible compared to the processing delay.
%\begin{equation}
%T^{\text{\text{tot}}} \approx T^{\text{proc}}
%\end{equation}
\subsubsection{Processing Delay}
Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ service (or slice).
Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^U = \sum_{u=1}^{U_s}\lambda_{u(s,i)}$.
Assume the mean arrival data rate of the UPF layer for slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and the O-DU ($\alpha_{s}^D$). so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$,
Because the amount of data traffic transferred along the route (regardless of frame changes) is constant.
Since, by using Burke’s theorem, the mean arrival data rate of the second and third layers, which are processed in the first layer, is still poisson with rate $\alpha_{s}$.
It is assumed that there are load balancers in each layer for each service to divide the incoming traffic to VNFs equally. %\cite{frdl,luong2018novel,luong2018novel1}.
Suppose the baseband processing of each VNF is depicted as M/M/1 processing queue.
Each packet is processed by one of the VNFs of a slice. So, the mean delay for the $s^{th}$ slice in the O-DU, the O-CU, and the UPF is modeled as M/M/1 queue, is formulated as follows, respectively \cite{SystemCostMinimization,luong2018joint,luong2018novel},
\begin{equation}
\begin{split}
T_{s}^{DU} &= \frac{1}{\mu_s^d - \alpha_{s}/{M_s^{d}}},\\
T_{s}^{CU} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}},\\
T_{s}^{UPF} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}},
\end{split}
\end{equation}
where $M_s^{d}$, $M_s^{c}$ and
$M_s^{u}$ are the variables that depict the number of VNFs in O-DU, O-CU-UP and UPF, respectively.
Moreover, $1/\mu_s^d$, $1/\mu_s^c$, and $1/\mu_s^u$ are the mean service time of the O-DU, O-CU, and the UPF layers, respectively.
Besides, $\alpha_{s}$ is the  arrival rate which is divided
by load balancer before arriving to the VNFs. The arrival rate of each VNF in each layer for each slice
$s$ is $\alpha_{s}/{M_s^{i}}$ $ i \in \{d,c, u\}$.

@@

\subsection{Slice Management}
In this subsection, we will look at the life cycle of network slicing on a practical level. 
The goal is to examine slice management, which includes creating, managing, and deleting slices. Network slices generally have four life cycle stages: preparation, commissioning, operation, and decommissioning \cite{ETSI2}.
\begin{itemize}
\item Preparation phase: The network slice instance (NSI) does not exist in the preparation phase. In this phase, the operator plans to create an NSI, such as designing the NSI template, onboarding users, and preparing the environment. Also, the evaluation of requirements is performed in this step.
\item Commissioning phase: in the commissioning phase, the creation of the NSI is done. In this phase, the requirements are considered and allocated to the slice.
\item Operation phase: during the Operation phase, NSIs are activated, managed, monitored (e.g., KPIs), modified, and deactivated. As the slice enters the activated phase, it is ready to support services, and as the slice exits the de-activated phase, the slice is inactive, and communication services are stopped.
\item Decommissioning phase: an NSI that is decommissioned no longer exists after this phase.
\end{itemize}
\textcolor{MidnightBlue}{In the preparation phase, firstly, the evaluation of requirements is considered. Therefore, In this phase, we need an algorithm to estimate the number of UEs and UE traffic in the system at different times. Moreover, based on this estimation, we need to evaluate resources, including the optimal number of VNFs for each slice, the optimal number of PRBs for each slice, and the analysis of power allocation. In this phase, we can use our algorithm after estimating the system's traffic.
As shown in figure 1, we have three different slices for eMBB, URLLC, and mMTC. For each slice, the system must prepare MAC/RLC protocols for O-DU, PDCP/SDAP protocols for O-CU, UPF, SMF, and AMF. Moreover, O-RU, high PHY in O-DU, and O-CU-CP are shared between slices. Thus, we do not require estimating and preparing for the share environments and platforms in the network slicing cycles.  
After evaluating, assessing, and preparing the resources and environments for each slice, the commissioning phase is started. In this phase, the slices are created based on the previous phase. If the evaluation changes, the slice's resources can be modified.
We can use our algorithm to assign resources to the services in the operation phase.
If we need to remove a slice or any service is not used in a zone, and we need to remove the corresponding slice, the unshared resources are removed in the decommissioning phase.}
%\vspace*{-1em}
\section{Proposed Algorithm}\label{proAlg}
In this section, we first apply some simplifications to the system; Solving the problem \eqref{problem} is complicated since this is non-convex mixed-integer non-linear problem (MINLP) with a binary variable and an integer variable.
We applied some simplifications and use an iterative heuristic algorithm to solve the problem.
We solve this problem in two levels, iteratively, until it converges \cite{ali2018joint}.

@@

\begin{subequations}\label{RM}

@@

\varpi_{u(s,i)} &= \lambda_{u(s,i)} + \frac{1}{T^{max}_s},\\

@@

@@

\begin{equation}\label{deriveP}
\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} &= (\delta_s + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k}\\
 &+ (\mathfrak{s}^k_{r,u(s,i)} -\mathfrak{D}_{r,u(s,i)}^{k})=0,\\

@@

p_{r,u(s,i)}^{k} &= [\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{ \text{Ln2} \times (-\mathfrak{s}^k_{r,u(s,i)} +\mathfrak{D}_{r,u(s,i)}^{k})}\\
 &-\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}]^+.
Also $[a]^+ = \max(0,a)$.
In addition, PRB assignment can be achieved from the derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{E}$ as follow.
\begin{subequations}\label{deriveE}
\dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} &= \mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})\\
&- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r\\
&+( \xi^{k}_{r,u(s,i)}-\mathfrak{v}^{k}_{r,u(s,i)} +\chi_{r,u(s,i)})=0.
So, the optimal $\boldsymbol{E}$ is obtained using KKT condition as follow.
\begin{equation}\label{deriveE1}
e_{r,u(s,i)}^{k} &\times (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}\\
& - \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r ) = 0.\\
where $\mathfrak{F}^{k}_{r,u(s,i)} =\mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})+( \xi^{k}_{r,u(s,i)} +\chi_{r,u(s,i)}) $.
Hence, from equation \eqref{deriveE} and \eqref{deriveE1}, PRB assignment is performed as follow.
e_{r,u(s,i)}^{k} =
  \begin{cases}
      1 & u(s,i) = \text{argmax} \mathfrak{Z}^{k}_{r,u(s,i)} \forall r, k \in K, s \in S, \\
      0 & \text{otherwise,}
    \end{cases}
where $\mathfrak{Z}^{k}_{r,u(s,i)} = (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r )$.
Thus, the user in slice $s$ that has  the most considerable value of $\mathfrak{F}^{k}_{r,u(s,i)}$, should be allocated to PRB $k$. Since just one PRB can be allocated to a UE between those UEs (regardless of the services), that is associated to the same O-RU.
The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$. Also, assume that the algorithm converges after $T_{conv}$ times.
The complexity order of this problem is about $O( T_{conv} \times\mathfrak{N} \times K)$.
\subsection{Sub-Problem 2}\label{sub2}
After power allocation and PRB assignment, the remaining problem is to assign O-RU to each UE in each service.

@@

Assume we have six 4-antenna O-RU (MISO) located in a place with a diameter of 500 meters as shown in figure \ref{fig:cell}. In addition, we consider the users placed randomly in this area.

@@

  \begin{tabular}{||c | c ||}
  \hline

>>>>

\begin{figure}
  \centering
  \captionsetup{justification=centering}
    \includegraphics[scale = 0.39]{finalDraw1.pdf}
    %\includegraphics[width=9.cm,height=6.2cm]{finalDraw1.pdf}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Network sliced O-RAN system}
  \label{fig:c11}
\end{figure}
\subsection{Motivation}
\textcolor{MidnightBlue}{The problem of finding the optimal resource allocation, independently of the specific RAN technology, is vital for reducing the cost of the system and improving the QoS of the user equipments (UEs). In case of 5G systems, there are many related significant challenges such as interference alignment, limited capacity of fronthaul links, energy restrictions on virtual machines, etc \cite{lee2018dynamic,SystemCostMinimization, setayesh2020joint}.}

@@

Multiplexing eMBB and URLLC services on the same RAN is particularly challenging, which has motivated some recent works.
In \cite{setayesh2020joint}, the problem of resource allocation in the coexistence of URLLC and eMBB services is considered to maximize the sum rate by ensuring that each user's traffic load demand is met and the slice isolation is guaranteed.
In \cite{yang2020should} a RAN slicing is considered in the coordinated multipoint system for eMBB and URLLC services to guarantee their QoS and reliability of URLLC. Moreover, \cite{saggese2021power} investigates the minimization of the system's power in the downlink RAN slicing of eMBB and URLLC services using non-orthogonal multiple access technique.
In \cite{alsenwi2021intelligent}, the problem of resource allocation for joint eMBB and URLLC services is formulated and solved by deep reinforcement learning.
% In \cite{korrai2020ran}, the authors proposed to allocate RAN resources for the network slicing system in the coexistence of eMBB and URLLC services. The system guarantees latency, service rate, and reliability maintenance.

In \cite{SystemCostMinimization,guo2016exploiting}, the authors address the issue of beamforming and VMs activation (using virtualization) in a C-RAN system with limited fronthaul capacity.
Paper \cite{SystemCostMinimization} aims to minimize the energy cost with the system delay, fronthaul capacity, and rate constraint.
Also, transmission and processing delays are modeled based on M/M/1 queueing theory to guarantee UE delays.
In \cite{luong2018joint,luong2018novel}, the problem of joint virtual computing resource allocation with beamforming is formulated. Also, the association of RRH to the UE is considered and solved using innovative methods.

In \cite{ali2019energy,ali2019energy1,ali2018joint}, the problem of joint power allocation and RRH association in a H-CRAN system is considered to maximize the energy efficiency.
Finally, in \cite{amani2019power}, the optimum power is obtained in the massive MIMO aided C-RAN system, and the problem of RRH to BBU and RRH to UE association is formulated and solved.

@@

A UE in an O-RU $r$ using PRB $k$ receives interference from other O-RUs in the set of $r' \in R \not\in r$ that are using the same PRB $k$. Two types of interference occur between UEs in each slice: i) inter-slice interference between signals transmitted over different slices, and ii) intra-slice interference between signals transmitted over the same slice that is shown in Fig. \ref{fig:intf}.

Network Slicing techniques significantly reduce inter-service interference.
Some methods apply the network slicing technique in PRB scheduling to isolate PRBs in slices and remove inter-slice interference. One of these methods is to have two-time scale scheduling. The PRB scheduling to the slices is performed on the first time scale, and on the second time scale, the PRB scheduling to the UEs of slices is carried out. Since there are limited resources, inter-service interference cannot be eliminated entirely. The other method is to allocate part of the RB of eMBB services to URLLC, and mMTC \cite{alsenwi2021intelligent, setayesh2020joint, mei2021intelligent}. In this paper, we assume that the PRB scheduling is performed. Also, in subsection \ref{prb}, we briefly study the PRB scheduling between slices.
\begin{figure}
  \centering
  \captionsetup{justification=centering}
    \includegraphics[scale = 0.35]{Interference.png}
    %\includegraphics[max height=30cm,max width=9.5cm]{Drawing15.eps}
    %\includegraphics[width=\textwidth]{finalDraw.pdf}
  \caption{Type of Interference Signal}
  \label{fig:intf}
\end{figure}
 $I_{r,u(s,i)}^{k}$ is the sum of the power of interfering signals and quantization noise represented as
%{\color{red} use paranthesis in the following equation to clear +}
%\begin{subequations}\label{eqI}
%\begin{alignat}{4}
\begin{align}\label{eqI}
&I_{r,u(s,i)}^{k} =\nonumber\\
 &\underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} e^{k}_{u(s,i)}e^{k}_{u(s,l)}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}+\nonumber\\
&\underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} e^{k}_{u(s,i)}e^{k}_{u(n,l)}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\nonumber\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
\end{align}
%\end{alignat}
%\end{subequations}
%{\color{red} $\gamma_1$ is constant used instead of variable. }
%where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
where $e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU. %($\gamma_1$ and $\gamma_2$ are two variales. You  define on variable here.)
Furthermore, there is no inter-slice interference since slices are isolated. Therefore, there exist only intra-slice interference.

@@

Moreover, ${x_P}$ denotes the precoded message before compression, and ${x_Q}$ illustrates the precoded message after compression shown in Fig. \ref{fig:pq}.

@@

\begin{subequations}\label{eq3}

@@

\mathcal{R}_{r, u(s_1,i)} &= \sum_{k=1}^{K} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}} e^k_{r,u(s_1,i)}),\\
\mathcal{R}_{u(s_1,i)} &= \sum_{r=1}^{R}\mathcal{R}_{r,u(s_1,i)} g^r_{u(s_1,i)},

@@

So, we assume that the total delay is approximate to the processing delay ($T^{\text{\text{tot}}} \approx T^{\text{proc}}$).
%Here we assume the propagation delay and the transmission delay are negligible compared to the processing delay.
%\begin{equation}
%T^{\text{\text{tot}}} \approx T^{\text{proc}}
%\end{equation}
\subsubsection{Processing Delay}
Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ service (or slice).
Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^U = \sum_{u=1}^{U_s}\lambda_{u(s,i)}$.
Assume the mean arrival data rate of the UPF layer for slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and the O-DU ($\alpha_{s}^D$). so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$,
Because the amount of data traffic transferred along the route (regardless of frame changes) is constant.
Since, by using Burke’s theorem, the mean arrival data rate of the second and third layers, which are processed in the first layer, is still poisson with rate $\alpha_{s}$.
It is assumed that there are load balancers in each layer for each service to divide the incoming traffic to VNFs equally. %\cite{frdl,luong2018novel,luong2018novel1}.
Suppose the baseband processing of each VNF is depicted as M/M/1 processing queue.
Each packet is processed by one of the VNFs of a slice. So, the mean delay for the $s^{th}$ slice in the O-DU, the O-CU, and the UPF is modeled as M/M/1 queue, is formulated as follows, respectively \cite{SystemCostMinimization,luong2018joint,luong2018novel},
\begin{subequations}
\begin{alignat}{4}
T_{s}^{DU} &= \frac{1}{\mu_s^d - \alpha_{s}/{M_s^{d}}},\\
T_{s}^{CU} &= \frac{1}{\mu_s^c - \alpha_{s}/{M_s^{c}}},\\
T_{s}^{UPF} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}},
\end{alignat}
\end{subequations}
where $M_s^{d}$, $M_s^{c}$ and
$M_s^{u}$ are the variables that depict the number of VNFs in O-DU, O-CU-UP and UPF, respectively.
Moreover, $1/\mu_s^d$, $1/\mu_s^c$, and $1/\mu_s^u$ are the mean service time of the O-DU, O-CU, and the UPF layers, respectively.
Besides, $\alpha_{s}$ is the  arrival rate which is divided
by load balancer before arriving to the VNFs. The arrival rate of each VNF in each layer for each slice
$s$ is $\alpha_{s}/{M_s^{i}}$ $ i \in \{d,c, u\}$.

@@

\subsection{Slice Management}
In this subsection, we will look at the life cycle of network slicing on a practical level. 
The goal is to examine slice management, which includes creating, managing, and deleting slices. Network slices generally have four life cycle stages: preparation, commissioning, operation, and decommissioning \cite{ETSI2}.
\begin{itemize}
\item Preparation phase: The network slice instance (NSI) does not exist in the preparation phase. In this phase, the operator plans to create an NSI, such as designing the NSI template, onboarding users, and preparing the environment. Also, the evaluation of requirements is performed in this step.
\item Commissioning phase: in the commissioning phase, the creation of the NSI is done. In this phase, the requirements are considered and allocated to the slice.
\item Operation phase: during the Operation phase, NSIs are activated, managed, monitored (e.g., KPIs), modified, and deactivated. As the slice enters the activated phase, it is ready to support services, and as the slice exits the de-activated phase, the slice is inactive, and communication services are stopped.
\item Decommissioning phase: an NSI that is decommissioned no longer exists after this phase.
\end{itemize}
\textcolor{MidnightBlue}{In the preparation phase, firstly, the evaluation of requirements is considered. Therefore, In this phase, we need an algorithm to estimate the number of UEs and UE traffic in the system at different times. Moreover, based on this estimation, we need to evaluate resources, including the optimal number of VNFs for each slice, the optimal number of PRBs for each slice, and the analysis of power allocation. In this phase, we can use our algorithm after estimating the system's traffic.
As shown in Fig. 1, we have three different slices for eMBB, URLLC, and mMTC. For each slice, the system must prepare MAC/RLC protocols for O-DU, PDCP/SDAP protocols for O-CU, UPF, SMF, and AMF. Moreover, O-RU, high PHY in O-DU, and O-CU-CP are shared between slices. Thus, we do not require estimating and preparing for the share environments and platforms in the network slicing cycles.  
After evaluating, assessing, and preparing the resources and environments for each slice, the commissioning phase is started. In this phase, the slices are created based on the previous phase. If the evaluation changes, the slice's resources can be modified.
We can use our algorithm to assign resources to the services in the operation phase.
If we need to remove a slice or any service is not used in a zone, and we need to remove the corresponding slice, the unshared resources are removed in the decommissioning phase.}
%\vspace*{-1em}
\section{Proposed Algorithm}\label{proAlg}
In this section, we first apply some simplifications to the system; Solving the problem \eqref{problem} is complicated since this is non-convex mixed-integer non-linear problem (MINLP) with a binary variable and an integer variable.
We applied some simplifications and use an iterative heuristic algorithm to solve the problem.
We solve this problem in two levels, iteratively, until it converges \cite{ali2018joint}.

@@

%\begin{subequations}\label{RM}
\begin{align}\label{RM}

@@

\varpi_{u(s,i)} &= \lambda_{u(s,i)} + \frac{1}{T^{max}_s}\nonumber\\

@@

\end{align}
%\end{subequations}

@@

\begin{align}\label{deriveP}
\dfrac{\partial\mathcal{L}}{\partial p_{r,u(s,i)}^{k}} &= (\delta_s + \mathfrak{h}_{u_{(s,i)}})\mathfrak{B}_{r,u(s,i)}^{k}\nonumber\\
 &+ (\mathfrak{s}^k_{r,u(s,i)} -\mathfrak{D}_{r,u(s,i)}^{k})=0,
\end{align}

@@

\begin{align}
p_{r,u(s,i)}^{k} &= \bigg[\frac{(\delta_s + \mathfrak{h}_{u_{(s,i)}})B \mathfrak{j}_{r,u(s,i)}^{k}}{ \text{Ln2} \times (-\mathfrak{s}^k_{r,u(s,i)} +\mathfrak{D}_{r,u(s,i)}^{k})} \nonumber\\
 &-\frac{BN_0 + I_{r,u(s,i)}^{k}}{{|\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2\mathfrak{j}_{r,u(s,i)}^{k}}\bigg]^+.
\end{align}

Also $[a]^+ = \max(0,a)$.
In addition, PRB assignment can be achieved from the derivatives of the Lagrangian function \eqref{lagrang} with respect to the $\boldsymbol{E}$ as follow.
\begin{align}\label{deriveE}
\dfrac{\partial\mathcal{L}}{\partial e_{r,u(s,i)}^{k}} &= \mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})\nonumber\\
&- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r\nonumber\\
&+( \xi^{k}_{r,u(s,i)}-\mathfrak{v}^{k}_{r,u(s,i)} +\chi_{r,u(s,i)})=0.
\end{align}
So, the optimal $\boldsymbol{E}$ is obtained using the KKT conditions, which require solving
\begin{align}\label{deriveE1}
e_{r,u(s,i)}^{k} &\times (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}\nonumber\\
& - \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r ) = 0,
\end{align}
where $\mathfrak{F}^{k}_{r,u(s,i)} =\mathcal{\bar{R}}_{r,u(s,i)}^{k}(\delta_s+\mathfrak{h}_{u_{(s,i)}})+( \xi^{k}_{r,u(s,i)} +\chi_{r,u(s,i)}) $.
Hence, from equation \eqref{deriveE} and \eqref{deriveE1}, PRB assignment is performed as follows
\begin{equation}
e_{r,u(s,i)}^{k} =
  \begin{cases}
      1 & u(s,i) = \text{argmax} \mathfrak{Z}^{k}_{r,u(s,i)} \forall r, k \in K, s \in S, \\
      0 & \text{otherwise,}
    \end{cases}
\end{equation}
where $\mathfrak{Z}^{k}_{r,u(s,i)} = (\mathfrak{F}^{k}_{r,u(s,i)} -\mathfrak{v}^{k}_{r,u(s,i)}- \mathfrak{m}_{r}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r )$.
 \end{proof}
Thus, the user in slice $s$ that has  the most considerable value of $\mathfrak{F}^{k}_{r,u(s,i)}$, should be allocated to PRB $k$. Since just one PRB can be allocated to a UE between those UEs (regardless of the services), that is associated to the same O-RU.
The number of UEs are $\mathfrak{N} = \sum_{s=1}^{S}\sum_{i=1}^{U_S}1$. Also, assume that the algorithm converges after $T_{conv}$ times.
The complexity order of this problem is about $O( T_{conv} \times\mathfrak{N} \times K)$.
\subsection{Sub-Problem 2}\label{sub2}
After power allocation and PRB assignment, the remaining problem is to assign O-RU to each UE in each service.

@@

Assume we have six 4-antenna O-RU (MISO) located in a place with a diameter of 500 meters as shown in Fig. \ref{fig:cell}. In addition, we consider the users placed randomly in this area.

@@

  \begin{tabular}{c  c }
  \toprule
